CS6213 Project Report

### 2021-05-07 report/paper.tex
WIP

However, we realised that in fact we are \emph{not} interested in exploring the state space. 
%
Since we are not doing model-checking, but rather counterexample finding, we can be very selective in terms of the states we explore.

Concretely, looking at our property, we see that it is somehow composed of distinct parts:
%
first, there is a trace prefix that leads to two leaders existing at the same time (in different terms; this is allowed in Raft),
%
then, some entry commits,
%
then afterwards, some more steps are taken, and there are still two leaders.

>>>>

However, we realised that in fact we are \emph{not} interested in exploring the state space. 
%
Since we are not doing model-checking, but rather counterexample finding, we can be very selective in terms of the states we explore.
%
Concretely, looking at our property, we see that it is somehow composed of distinct parts:
%
(1) first, there is a trace prefix that leads to two leaders existing at the same time (in different terms; this is allowed in Raft),
%
(2) then some entry commits,
%
(3) a few more steps are taken, and there are still two leaders.

The insight is that we can explore the state space using TLC's default breadth-first search to find \emph{a} trace $T$ satisfying (1), restart the BFS taking $T$ as the initial state to find a state satisfying (2), and then repeat the process to find a state satisfying (3).

As we noted previously, this approach is similar to concolic execution:
%
when the search space gets too large to handle, we concretise to a single state and resume search from that point.
%
We implemented this ``manually'' by running with (1) as a goal, copying the concrete state found by TLC and adding it as a constraint, and then restarting TLC with (2) as a goal, and so on.
%
But this seems like it would be easy to implement directly in TLC.
